---
title: "Update 2 stat479"
author: "Marshall Bennett"
date: "February 1, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

#New code
dest= rep("", 52)
for(i in 1:52) dest[i]=paste("https://www.fhwa.dot.gov/bridge/nbi/2016/delimited/", states[i,2],"16.txt", sep = "") 
x16 = ldply(dest, fread, colClasses = classes) 
save(x16, file = "bridgesdata.RData")
keep = c("STATE_CODE_001",  "FEATURES_DESC_006A", "STRUCTURE_NUMBER_008" , "COUNTY_CODE_003", "LAT_016", "LONG_017", "TOLL_020" ,"YEAR_BUILT_027", "ADT_029","YEAR_ADT_030"
         , "DECK_COND_058" , "SUPERSTRUCTURE_COND_059", "SUBSTRUCTURE_COND_060"  , "CHANNEL_COND_061","CULVERT_COND_062", "DATE_OF_INSPECT_090",  "OPERATING_RATING_064")
M=x16
# x = M[,match(keep, colnames(M))]
M = as.tbl(M)
x = select(M, one_of(keep))
library(ggplot2)
x = mutate(x, fips = STATE_CODE_001*1000+COUNTY_CODE_003)
#It's interesting to see that there are quite a few counties
#with very high numbers of bridges

hist(x$fips)
#The condition variables will be the excellent way to rate
#the bridges, but first the N values should be replaced with
#10, for the highest value
x$DECK_COND_058[which(x$DECK_COND_058 == "N")]= 10
x$SUPERSTRUCTURE_COND_059[which(x$SUPERSTRUCTURE_COND_059 == "N")]= 10
x$SUBSTRUCTURE_COND_060 [which(x$SUBSTRUCTURE_COND_060 == "N")]= 10
x$CHANNEL_COND_061[which(x$CHANNEL_COND_061 == "N")]= 10
x$CULVERT_COND_062[which(x$CULVERT_COND_062 == "N")]= 10
x = mutate(x, cond = as.numeric(x$DECK_COND_058)+as.numeric(x$SUPERSTRUCTURE_COND_059)+ as.numeric(x$SUBSTRUCTURE_COND_060)+ as.numeric(x$CHANNEL_COND_061)+as.numeric(x$CULVERT_COND_062))

#Stole Karl's function to suit my needs
rateIt = function(cond){
  # gives a good to fail rating for cond.
  rate = rep("new", length(cond))
  rate[cond<40] = "Like New"
  rate[cond <30]= "Average"
  rate[cond <20]= "Poor"
  rate[cond < 10] = "Failure"
  return(rate)
}
x$rate = rateIt(x$cond)
old = filter(x, x$YEAR_BUILT_027<1940)
war = filter(x, x$YEAR_BUILT_027>1940 & x$YEAR_BUILT_027<1946)
new = filter(x, x$YEAR_BUILT_027>1946)
hist(old$cond)
hist(war$cond)
hist(new$cond)
#This plot is very time consuming, but it accurately plots
#the ages and conditions of the bridges, with the rating 
#used as the color of the different dots.
ggplot(x, aes(YEAR_BUILT_027, cond))+geom_point(aes(colour = rate))
#Itis clear from the subsequent graph that the majority of
#the bridges are doing well, in the mid to upper 40s.
ggplot(x) + geom_bar(mapping = aes(x=cond))



